---
title: "Ask Cinderhaven — `r params$question`"
format:
  pdf:
    documentclass: article
    geometry:
      - top=0.8in
      - bottom=0.8in
      - left=0.8in
      - right=0.8in
    fontsize: 11pt
    include-in-header:
      - text: |
          \usepackage{xcolor}
          \definecolor{navy}{HTML}{1f2e7a}
          \definecolor{teal}{HTML}{158f75}
          \definecolor{gridline}{HTML}{d9d9d9}
          \definecolor{textsec}{HTML}{595959}
execute:
  echo: false
params:
  question: ""
  verdict: ""
  verdict_detail: ""
  key_numbers_json: "[]"
  rule_explanation: ""
  go_deeper_link: ""
  go_deeper_label: ""
  scenario: "baseline"
  source_piece: ""
---

```{r}
#| include: false
# Escape LaTeX special chars for content output into raw LaTeX blocks.
tex_esc <- function(x) {
  x <- gsub("\\\\", "\\\\textbackslash{}", x)
  x <- gsub("$", "\\$", x, fixed = TRUE)
  x <- gsub("%", "\\%", x, fixed = TRUE)
  x <- gsub("&", "\\&", x, fixed = TRUE)
  x <- gsub("#", "\\#", x, fixed = TRUE)
  x <- gsub("{", "\\{", x, fixed = TRUE)
  x <- gsub("}", "\\}", x, fixed = TRUE)
  x
}
```

```{r}
#| results: asis
# Output as {=latex} raw block so pandoc passes it verbatim — avoids $ / % misparse.
cat(paste0("```{=latex}\n",
           "\\textcolor{textsec}{\\small\\textit{",
           tex_esc(params$scenario), " scenario --- figures reconcile to ",
           tex_esc(params$source_piece), "}}\n",
           "```\n"))
```

\vspace{0.3in}

## `r params$question`

\vspace{0.1in}

```{r}
#| results: asis
cat(paste0("```{=latex}\n",
           "\\textcolor{navy}{\\textbf{", tex_esc(params$verdict), "}}\n",
           "```\n"))
```

\vspace{0.2in}

---

### How this verdict was reached

`r params$rule_explanation`

\vspace{0.2in}

### Go deeper

`r params$go_deeper_label`: `r params$go_deeper_link`

\vspace{0.5in}

\footnotesize\textcolor{textsec}{Built by Lailara LLC --- data hygiene and analytics consulting for specialty food brands scaling into national retail. lailarallc.com}
